### 2019-06-12 thesis-template/msc-thesis.tex
update

\textbf{Symmetric Tensor Field Visualization}\\
Zheng \& and Pang \cite{pang&zheng} et al. proposed a texture-based visualization approach called Hyper LIC, which extends the concept of LIC to symmetric tensor fields by using an anisotropic 2D-filter kernel oriented along the major/minor eigenvectors. The concept of following the major/minor eigenvector along tensor field lines was invented by Vilanova et al. \cite{vilanova}. Tensorlines introduce a kind of artificial inertia (running average), making them resistent to noise. The notion of tensor field topology (critical, degenerate points, separatrices) and the concept of Hyperstreamlines was first introduced by Delmarcelle and Hesselink \cite{delmarcelle&hesselink}. The placement of tensor field lines as hyperstreamlines was recently improved by Spencer et al. \cite{spencer} for glyph packing. A good overview of seeding strategies concerning glyphs is given by McLoughlin et al. \cite{mcloughlin}. Feng et al. \cite{feng} used Voronoi Tesselation for placing the glyphs. Superquadric glyphs have been proposed by Schultz and Kindlmann \cite{schultz&kindlmann} for general (non-positive definite) tensors. De Leeuw and van Wijk \cite{deleeuw&vanwijk} visualize the partial derivative gradient, the Jacobian of the tensor field to sense the local properties of the field. A diffusion tensor can also be visualized by box \cite{makris}, ellipsoid \cite{pierpaoli}, composite \cite{westin2} or superquadric \cite{kindlmann} glyphs. There is also a set of scalar measures available in symmetric tensor field visualization such as: mean diffusivity, fractional anisotropy \cite{basser} and anisotropy coefficients \cite{westin}. These coefficients can also be visualized by direct volume rendering \cite{kindlmann2}. Hlawatsch et al. \cite{hlawatsch} obtain a coordinate (flow) map from tensor field lines following major/minor eigenvectors (fibre trajectories) and use the maximum eigenvalue of the Cauchy-Green deformation tensor to compute the FTLE-field in homogeneous regions. In a similar manner, we aim to use light transport techniques to obtain a final light distribution through successive light propagation cycles footprinted (in form of transmission profiles obtained from ellipsoid glyphs) by the tensor field. DT-MRI diffusion tensor imaging can help to reveal the functional \cite{denis} or topological \cite{wakana} structure of the brain and muscles by analysing celebral and muscle tissue tractography which yields a tensor field of the anisotropy of the brain's white matter. An overview about DT-MRI visualization techniques is given by \cite{vilanova}
\\
\textbf{Asymmetric Tensor Field Visualization}\\
Zheng and Pang \cite{pang&zheng} proposed the concept of dual eigenvectors and Zhang et al. \cite{zhang} extended it to pseudo-eigenvectors and introduced the eigenvector/eigenvalue manifolds to visualize eigenvectors in the complex domain. Laramee et al. \cite{laramee} focused on the efficient implementation and visualization of these structures and provided an interactive visualization system for asymmetric tensors applicable in fluid and solid dynamics. The concept of tensor magnitude has been introduced by \cite{laramee2} for means of physical interpretation. They also proposed an efficient glyph and hyperstreamline hybrid approach, which made dynamic interaction in real-time in 2D tensor fields feasible. Palacios et al. \cite{palacios} extracted isosurfaces of tensor magnitude, mode and isotropy index. \vskip 5pt

>>>>

\textbf{Symmetric Tensor Field Visualization}\\
Zheng \& and Pang \cite{pang&zheng} et al. proposed a texture-based visualization approach called Hyper LIC, which extends the concept of LIC to symmetric tensor fields by using an anisotropic 2D-filter kernel oriented along the major/minor eigenvectors. The concept of following the major/minor eigenvector along tensor field lines was invented by Vilanova et al. \cite{vilanova}. Tensorlines \cite{weinstein} introduce a kind of artificial inertia (running average), making them resistent to noise. The notion of tensor field topology (critical, degenerate points, separatrices) and the concept of Hyperstreamlines was first introduced by Delmarcelle and Hesselink \cite{delmarcelle&hesselink}. The topology in $3D$ tensor fields was first analyzed by \cite{zheng}. The placement of tensor field lines as hyperstreamlines was recently improved by Spencer et al. \cite{spencer} for glyph packing. A good overview of seeding strategies concerning glyphs is given by McLoughlin et al. \cite{mcloughlin}. Feng et al. \cite{feng} used Voronoi Tesselation for placing the glyphs. Superquadric glyphs have been proposed by Schultz and Kindlmann \cite{schultz&kindlmann} for general (non-positive definite) tensors. De Leeuw and van Wijk \cite{deleeuw&vanwijk} visualize the partial derivative gradient, the Jacobian of the tensor field to sense the local properties of the field. A diffusion tensor can also be visualized by box \cite{makris}, ellipsoid \cite{pierpaoli}, composite \cite{westin2} or superquadric \cite{kindlmann} glyphs. There is also a set of scalar measures available in symmetric tensor field visualization such as: mean diffusivity, fractional anisotropy \cite{basser} and anisotropy coefficients \cite{westin}. These coefficients can also be visualized by direct volume rendering \cite{kindlmann2}. Hlawatsch et al. \cite{hlawatsch} obtain a coordinate (flow) map from tensor field lines following major/minor eigenvectors (fibre trajectories) and use the maximum eigenvalue of the Cauchy-Green deformation tensor to compute the FTLE-field in homogeneous regions. In a similar manner, we aim to use light transport techniques to obtain a final light distribution through successive light propagation cycles footprinted (in form of transmission profiles obtained from ellipsoid glyphs) by the tensor field. DT-MRI diffusion tensor imaging can help to reveal the functional \cite{denis} or topological \cite{wakana} structure of the brain and muscles by analysing celebral and muscle tissue tractography which yields a tensor field of the anisotropy of the brain's white matter. An overview about DT-MRI visualization techniques is given by \cite{vilanova}. Tricoche et al. \cite{xavier} use invariant manifolds to extract topological features from tensor fields. Other, feature extraction based approaches extract general features as: edges \cite{hancock}, tensor shape\/ orientation \cite{gordon}, interfaces \cite{donnel}, creases \cite{tricochet}.
\\
\textbf{Asymmetric Tensor Field Visualization}\\
Zheng and Pang \cite{pang&zheng} proposed the concept of dual eigenvectors and Zhang et al. \cite{zhang} extended it to pseudo-eigenvectors and introduced the eigenvector/eigenvalue manifolds to visualize eigenvectors in the complex domain. Laramee et al. \cite{laramee} focused on the efficient implementation and visualization of these structures and provided an interactive visualization system for asymmetric tensors applicable in fluid and solid dynamics. The concept of tensor magnitude has been introduced by \cite{laramee2} for means of physical interpretation. They also proposed an efficient glyph and hyperstreamline hybrid approach, which made dynamic interaction in real-time in 2D tensor fields feasible. Palacios et al. \cite{palacios} extracted isosurfaces of tensor magnitude, mode and isotropy index. \vskip 5pt
